\documentclass[12pt]{article}%
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{comment}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2.2cm, right=2.2cm]%
{geometry}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{changepage}
\usepackage{amssymb}
%\usepackage{graphicx}%
\setcounter{MaxMatrixCols}{30}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}

\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}

\newcommand{\E}{\mathrm{E}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}

\begin{document}

\title{MATH618 Homework 5}
\author{Fernando}
\date{\today}
\maketitle
\section*{Problem 1}
\subsection*{$L_1+L_2$ is compact}
\textbf{Proof:}\\
Let $x_k$ be a bounded sequence. Since $L_1$ is compact we can find a
subsequence $x_{k_i}$ such that $L_1(x_{k_i})$ converges. Because $x_{k_i}$ is
also bounded we can find $x_{k_{i_j}}$ such that $L_2(x_{k_{i_j}})$ converges
(because $L_2$ is compact), and thus $(L_1+L_2)(x_{k_{i_j}})$ converges.\\
\textbf{Conclusion:} any bounded sequence under $L_1+L_2$
has a convergent subsequence. $\qedsymbol$
\subsection*{$\alpha L$ is compact}
\textbf{Proof:}\\
Let $x_k$ be a bounded sequence. Since $L$ is compact we can find a subsequence
$x_{k_i}$ such that $L(x_{k_i})$ converges, then clearly $\alpha
L(x_{k_i})$ is also convergent, hence $\alpha L$ is compact. $\qedsymbol$
\section*{Problem 2}
\textbf{Proof:}\\
Let $x_k$ be a bounded sequence. Since $A$ is compact we can find a
subsequence $x_{k_i}$ such that $A(x_{k_i})$ converges. Because $x_{k_i}$ is
also bounded we can find $x_{k_{i_j}}$ such that $B(x_{k_{i_j}})$ converges
(because $B$ is compact), and thus $AB(x_{k_{i_j}})$ converges. $\qedsymbol$
\section*{Problem 3}
\subsection*{Part a}
This operator is bounded because of Parseval's identity, i.e.
\[
	||f||_X = C ||Lf||_Y
\]
for some constant $C$. So any bounded sequence will be mapped to a
bounded sequence.
\subsection*{Part b}
This operator is bounded because of Parseval's identity, i.e.
\[
	||f||_Y=C||L^{-1}f||_X
\]
for some constant $C$. So any bounded sequence will be mapped to a
bounded sequence.
\subsection*{Part c}
$L$ is not compact because if we take $\{x_k\}$ where $x_k=\sin(kt)$ (bounded)
this sequences gets mapped to $\{e_k\}$ which we know is not precompact.

$L^{-1}$ is not compact basically for the same reason, $\{e_k\}$ (bounded) gets
mapped to $\{\sin(kt)\}$ which again we know is not precompact.
\section*{Problem 4}
We want to estimate (find a bound for)
\[
	A_k
	=\frac{||y_k-\tilde{y}_k||}{||y_k||}\bigg/\frac{||x_k-\tilde{x}_k||}{||x_k||}
	=\frac{||y_k-\tilde{y}_k||\cdot||x_k||}{||y_k||\cdot||x_k-\tilde{x}_k||}
	=\frac{||y_k-\tilde{y}_k||}{||x_k-\tilde{x}_k||} \cdot
	\frac{||x_k||}{||y_k||}
	=\frac{||L(\delta x_k)||}{||\delta x_k||} \cdot \frac{||x_k||}{||L(x_k)||}
\]
Then
\[
A_k=\frac{||L(\delta x_k)||}{||\delta x_k||} \cdot \frac{||x_k||}{||L(x_k)||}\leq
||L||\cdot \frac{||x_k||}{||L(x_k)||}
\]
For simplicity let's assume that $L$ is invertible (otherwise I am not sure how
to proceed), then we have
\[
A_k\leq
||L||\cdot \frac{||L^{-1}(x_k)||}{||x_k||} \leq ||L|| \cdot ||L^{-1}||.
\]
If $L$ was not bounded then $A_k \to \infty$ as $k \to \infty$ and that means
that small errors in our measurements will be amplified greatly as we increase
the dimension. This means that our end result \textbf{could} be completely
useless. That is why we need $L$ to be bounded.

In regards to $L^{-1}$ there is a theorem (bounded inverse theorem) that
ensures that under appropriate conditions if $L$ is a bijective bounded linear
operator then $L^{-1}$ is also bounded.
\section*{Problem 5}
For what I understood about this problem the intension is to use the empirical
evidence that we have from the world to answer instead of using a rigorous
mathematical argument.
\subsection*{Part a}
In class we talked about the fact that compact operators on infinite
dimensional spaces can't have bounded inverses because of the behavior of the
eigenvalues. Another way to see this is the following: It is not hard to prove
that the composition of a compact operator and a bounded operator is compact,
then for a compact $T$, if $T^{-1}$ was bounded, $TT^{-1}=I$ would be compact
but we know from a previous homework that this is not true.

By the previous problem we know that in order to implement $L$ and $L^{-1}$
both must be bounded. By the previous paragraph $L$ and $L^{-1}$ can't be both
compact.
\subsection*{Part b}
\subsection*{Part c}
\end{document}
